Notes on RBFs methods for Neural Fields

### 2023-11-14 Manuscript/manuscript.tex
Sentence about the quadrature rivisited

To complete the scheme, we now require a quadrature formula for the integrand. The
formula we employ is a composite formula over the Voronoi diagram
\[
  \begin{aligned}
  Q v := \int_{D} v(y)\,d \mu(y) 
    & = \sum_{j=1}^n \int_{D_j} v(y) \,d \mu(y) \\
    & \approx \sum_{j = 1}^n \int_{D_j} v_n(y) \,d \mu(y)
      \approx \sum_{j = 1}^n v(x_j) \mu_j =: Q_n v,
  \end{aligned}
\]
where the weights $\{ \mu_j \}_{j \in \NSet_n}$ satisfy
\da[inline]{Complete. I am unsure there are two approximation symbols above, or just
one. If possible, say something about the expected convergence rate of $|Qv - Q_nv|$.} 
We are now ready to specify a discrete scheme by applying the quadrature rule $Q_n$
the function $K$ in \cref{eq:NFODE}, recalling that each $D_i$ contains exactly
one node, namely $x_i$, and obtaining the spatially-discrete scheme
\[
  \begin{aligned}
  & \tilde \alpha'(t) = -\tilde \alpha(t) + \gamma(t) 
    + M f(\tilde \alpha(t)), \qquad t \in J \\
  & \tilde \alpha(0) = \nu
  \end{aligned}
\]
where $M_{ij} = w(x_i,x_j)\mu_j$, and in which we have used, with a little abuse of
notation, $f(\alpha)$ to denote the vector with components $(f(\alpha))_i =
f(\alpha_i)$. We have therefore provided an RBF example of the collocation scheme
\cref{eq:NFODEQuad}, in which $\tilde K(\tilde \alpha) = M f(\tilde \alpha)$.

>>>>

To complete the scheme, we now require a quadrature formula for the integrand. The
formula we employ is a composite formula over the Voronoi diagram
\[
  \begin{aligned}
  Q v := \int_{D} v(y)\,d \mu(y) 
    & = \sum_{j=1}^n \int_{D_j} v(y) \,d \mu(y) \\
    & \approx \sum_{j = 1}^n \int_{D_j} v_n(y) \,d \mu(y)
      \approx \sum_{j = 1}^n v(x_j) \mu_j =: Q_n v,
  \end{aligned}
\]
in which the integral over a cell $D_i$ is approximated using a single node $x_j$,
the centre of the cell, and a single weight $\mu_j$. The weights satisfy \ldots
\da[inline]{Complete. I am unsure there are two approximation symbols above, or just
one. That depends on how weights are calculated. If possible, we should say something
about the expected convergence rate of $|Qv - Q_nv|$.} We are now ready to specify a discrete scheme by applying the quadrature rule $Q_n$
the function $K$ in \cref{eq:NFODE}, recalling that each $D_i$ contains exactly
one node, namely $x_i$, and obtaining the spatially-discrete scheme
\[
  \begin{aligned}
  & \tilde \alpha'(t) = -\tilde \alpha(t) + \gamma(t) 
    + M f(\tilde \alpha(t)), \qquad t \in J \\
  & \tilde \alpha(0) = \nu
  \end{aligned}
\]
where $M_{ij} = w(x_i,x_j)\mu_j$, and in which we have used, with a little abuse of
notation, $f(\alpha)$ to denote the vector with components $(f(\alpha))_i =
f(\alpha_i)$. We have therefore provided an RBF example of the collocation scheme
\cref{eq:NFODEQuad}, in which $\tilde K(\tilde \alpha) = M f(\tilde \alpha)$.
